MCMC convergence diagnostics

### 2023-12-31 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Small change to MCMC, and make increase s, k output a figure for thesis appendix

```{r}
ggplot(df, aes(x = s, y = lognormconst)) +
  geom_point() +
  facet_grid(. ~ k) +
  labs(x = "Dimensions kept of the PCA", y = "Log normalising constant") +
  theme_minimal()
```

```{r}
ggplot(df, aes(x = s, y = time)) +
  geom_point() +
  facet_grid(. ~ k) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Dimensions kept of the PCA", y = "Time (mins)") +
  theme_minimal()
```

>>>>

```{r}
multi.utils::cbpalette()

df %>%
  pivot_longer(
    cols = c("lognormconst", "time"),
    values_to = "value",
    names_to = "indicator"
  ) %>%
  mutate(
    indicator = fct_recode(indicator,
      "Log normalising\nconstant estimate" = "lognormconst",
      "Time taken (m)" = "time"
    )
  ) %>%
  ggplot(aes(x = s, y = value, col = indicator)) +
    geom_point() +
    facet_grid(indicator ~ k, scales = "free") +
    labs(x = " PCA-AGHQ dimensions kept", y = "") +
    scale_color_manual(values = c("#009E73", "#E69F00")) +
    guides(col = "none") +
    theme_minimal()

ggsave("lognormconst.png", h = 4, w = 6.25, bg = "white")
```

### 2023-12-31 src/naomi-simple_mcmc/mcmc-convergence.Rmd
Small change to MCMC, and make increase s, k output a figure for thesis appendix

fig_top_left <- ggplot(pairs_df, aes(x = log_sigma_rho_a)) +
  geom_histogram(fill = "#56B4E9", col = "#1a88c6") +
  labs(x = "", y = "", tag = "A") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

fig_bot_right <- ggplot(pairs_df, aes(x = logit_phi_rho_a)) +
  geom_histogram(fill = "#56B4E9", col = "#1a88c6") +
  labs(x = "logit_phi_rho_a", y = "", tag = "D") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

fig_top_left <- ggplot(pairs_df, aes(x = log_sigma_alpha_x)) +
  geom_histogram(fill = "#56B4E9", col = "#1a88c6") +
  labs(x = "", y = "", tag = "A") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

fig_bot_right <- ggplot(pairs_df, aes(x = logit_phi_alpha_x)) +
  geom_histogram(fill = "#56B4E9", col = "#1a88c6") +
  labs(x = "logit_phi_alpha_x", y = "", tag = "D") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

>>>>

fig_top_left <- ggplot(pairs_df, aes(x = log_sigma_rho_a)) +
  geom_histogram(fill = "#56B4E9") +
  labs(x = "", y = "", tag = "A") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

fig_bot_right <- ggplot(pairs_df, aes(x = logit_phi_rho_a)) +
  geom_histogram(fill = "#56B4E9") +
  labs(x = "logit_phi_rho_a", y = "", tag = "D") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

fig_top_left <- ggplot(pairs_df, aes(x = log_sigma_alpha_x)) +
  geom_histogram(fill = "#56B4E9") +
  labs(x = "", y = "", tag = "A") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

fig_bot_right <- ggplot(pairs_df, aes(x = logit_phi_alpha_x)) +
  geom_histogram(fill = "#56B4E9") +
  labs(x = "logit_phi_alpha_x", y = "", tag = "D") + 
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
